Learning CNN filters from user-drawn image \textcolor{red}{markers} for coconut-tree image classification

### 2020-07-24 IEEE-GRSL-Response-Letter.tex

\rwr{2} Pg. 9 - Lines 14-18: Justify the choice of all hyperparameters (E.g. epochs, batch size, learning rate, etc). Have any previous experiments been made to tune these hyperparameters? Has the same dataset been used?

\ans Thanks to have pointed it out. We are now explaining that the dataset is randomly divided into training (200 images), validation (1000 images), and testing (remaining images) sets. We repeated each experiment three times, each using one of these random splits. However, the validation set was used only once to choose the hyperparameters of the network. We have not developed/used any optimization technique for this purpose. We have just executed tests with a few hyperparameter choices in order to select one for the experiments. The idea was to select the simplest and yet effective network in order to demonstrate that FLIM can create competitive solutions. We are clarifying this issue (Section III) and indicating it for future work (Section IV). 
\eans

\rwr{2} Pg. 10 - Table 1: The F-score difference from FLIM+MLP (0.854) and VGG+FT (0.851) is statistically significant considering the standard deviation?  Has a statistical hypothesis test been applied?

For three splits only and 200 training images, it was not possible to claim that this difference is statistically significant. However, they are undoubtedly competitive, being FLIM+MLP a much simpler (lighter) network than VGG-FT.   
\eans

@@

For three splits only and 200 training images, it was not possible to claim that this difference is statistically significant. However, they are undoubtedly competitive, being FLIM+MLP a much simpler (lighter) network than VGG-FT.   
\eans

\rwr{2} Pg. 11 - It would be worth investigating or discussing if the time taken to mark some images is always less than the time take to produce more labeled images (E.g.: how many new labeled images would take for VGG+FT beat FLIMP+MLP?). Is there a trade-off?

\ans Thanks a lot for raising both questions. We noticed that it was not clear that markers are drawn on a few images selected from the training set (we used only 4 images). The user takes a couple of minutes to select images and draw markers on those images. This time is much less than the time taken to examine and label 200 images. We added a sentence to clarify that in Section I. We also added Figure 3 to explain the user-interaction process in FLIM and modified a few parts in the text to clarify that FLIM is trained from markers in 4 images only.

We added an experiment with increasing training set sizes. VGG-FT could never beat FLIM+MLP, even with a higher number of training images to improve its features. The reason is that 1200 images were not enough to improve VGG-FE (the feature extractor obtained at the last convolutional layer of VGG-FT). Both FLIM+MLP and VGG-FT use a similar MLP (the only difference is in the input layer due to their different number of features). Therefore, the higher number of training images benefit both approaches, being the mean f-score curve of FLIM+MLP consistently above the one of VGG-FT.

@@

\eans

\rwr{2} Pg. 12 - It seems that the literature review outdated (only one 2019/2020 work and from the same authors).

\ans
Thanks, we have improved the literature review in Section I.
\eans

### 2020-07-25 main.tex
reviewing

\title{Learning CNN filters from user-drawn image markers for coconut-tree image classification}

@@

\section{Introduction}
\IEEEPARstart{D}{eep} learning has proven to be applicable to different tasks, from image classification to data synthesis \cite{goodfellow2016deep}. In remote sensing, the applications may involve segmentation of terrain images \cite{kemker2018algorithms, kampffmeyer2016semantic}, building identification \cite{xu2018building, lu2018detecting, liu2018multilevel}, and deforestation monitoring \cite{bragilevsky2017deep}, for instance. In this work, we are interested in identifying species of trees from aerial images. The topic is important for land-use classification, plantation monitoring, and damage assessment of natural disasters. As the plantations can span vast areas, the manual identification of each tree is costly, tedious, and error-prone, and so automatic classification methods are necessary.

@@

The design of CNN models without a human as part of the training loop leaves several questions unanswered: (1) How to find a useful and simplified model for a given classification problem? (2) How to train that model from a minimum number of annotated images?  (3) Can the user explain the decisions of the model? (4) Can the model improve from label corrections? The first question requires human knowledge about CNN modeling and the problem of interest. The second one requires to reduce the human effort to train a CNN model. The third issue is related to human understanding. It may explore visual analytics to explain the model's decisions and to guide the user in the design of the model~\cite{RauberInfoVis2018,GarciaIJCNN2019,SpinnerTVCG2020}. The fourth question is also essential during training, and it is related to user control over the process. They all lead to the importance of involving human experts during the machine learning process. \textcolor{red}{Explainable artificial intelligence (XAI) has appeared to address such problems~\cite{rauber2016visualizing,arrietaInfoFusion2020}. However, the importance of human participation during the training process has called little attention~\cite{AngelovNN2020}. Exceptions rely on visual analytics~\cite{RauberInfoVis2018,GarciaIJCNN2019,SpinnerTVCG2020}, and we present here a first work in which the user has direct influence over the quality of the filters.}

>>>>

\title{Learning CNN filters from user-drawn image \textcolor{red}{markers} for coconut-tree image classification}

@@

\section{Introduction}

\IEEEPARstart{D}{eep} learning has proven to be applicable to different tasks, from image classification to data synthesis \cite{goodfellow2016deep}. In remote sensing, the applications may involve segmentation of terrain images \cite{kemker2018algorithms, kampffmeyer2016semantic}, building identification \cite{xu2018building, lu2018detecting, liu2018multilevel}, and deforestation monitoring \cite{bragilevsky2017deep}, for instance. In this work, we are interested in identifying species of trees from aerial images. The topic is important for land-use classification, plantation monitoring, and damage assessment of natural disasters. As the plantations can span vast areas, the manual identification of each tree is costly, tedious, and error-prone, and so automatic classification methods are necessary.

@@

The design of CNN models without a human as part of the training loop leaves several questions unanswered: (1) How to find a useful and simplified model for a given classification problem? (2) How to train that model from a minimum number of annotated images?  (3) Can the user explain the decisions of the model? (4) Can the model improve from label corrections? The first question requires human knowledge about CNN modeling and the problem of interest. The second one requires to reduce the human effort to train a CNN model. The third issue is related to human understanding. It may explore visual analytics to explain the model's decisions and to guide the user in the design of the model~\cite{RauberInfoVis2018,GarciaIJCNN2019,SpinnerTVCG2020}. The fourth question is also essential during training, and it is related to user control over the process. They all lead to the importance of involving human experts during the machine learning process. \textcolor{red}{Explainable artificial intelligence (XAI) has appeared to address \textcolor{blue}{(3)}~\cite{rauber2016visualizing,arrietaInfoFusion2020}. However, the importance of human participation during the training process has called little attention~\cite{AngelovNN2020}. Exceptions rely on visual analytics~\cite{RauberInfoVis2018,GarciaIJCNN2019,SpinnerTVCG2020}, and we present here a first work in which the user has direct influence over the quality of the filters.}
